Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-09-05 manuscript/abstract.tex
Update main figures and key points in abstract outline

\begin{itemize}
\item{Phenotypic measurements of antigenic advance outperform genetic estimates from epitope mutations in long-term forecasts}
\item{DMS measurements enable more precise identification of mutationally intolerant sites to replace previous sites based on all non-epitope regions}
\item{Phylogenetic fitness metrics outperform and appear to be mutually exclusive of mechanistic metrics}
\item{Distance-based model target performs as well or better than clade-based targets and enables future forecasting efforts where phylogenies are not feasible}
\item{We provide (the first?) open source, extensible forecasting framework for influenza}
\end{itemize}

>>>>

\begin{itemize}
\item{Phenotypic measurements of antigenic advance outperform genetic estimates from epitope mutations in long-term forecasts}
\item{Phylogenetic fitness metrics outperform and appear to be mutually exclusive of mechanistic metrics}
\item{Fitness metrics based on epitope mutations are not robust to long-term changes in genetic background of successful populations}
\item{Fitness metrics based on DMS measurements overfit to the genetic background of the experimental strain}
\item{Distance-based model target performs as well or better than clade-based targets and enables future forecasting efforts where phylogenies are not feasible}
\item{We provide (the first?) open source, extensible forecasting framework for influenza}
\end{itemize}
